Import_JazEmData

### 2024-01-03 Code/Import_JazEmData.Rmd
Fixed code and nested df before saving .rds

# Set the path to the zip folder
zip_file <- file.path("..", "Data", "RawData", "JazEmData.zip")

# List files in the extracted folder with a ".txt" extension
Jazfile <- unzip(zip_file, list = TRUE)
Jazfile <- Jazfile[grepl(".txt$", Jazfile$Name), "Name"]
print(Jazfile)
```

# Set up fread_plus function
```{r set up fread_plus, warning = FALSE, echo=FALSE}
SkipCS <- 14
FileEncodeCS <- "UTF-8"
DelimCS <- "\t"
RollWindow <- 10

# Define function to read and process each file
fread_plus <- function(Flnm, Skip, FileEncode, Delim) {
  con <- unz(zip_file, Flnm)  # Connect to the file path within the zip archive
  data <- read.table(con, skip = Skip, encoding = FileEncode, sep = Delim, header = FALSE)

@@

  data <- data %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(zip_file)$ctime)) 
  return(data)
}

@@

# Import and tidy columns
```{r filename separation, warning = FALSE, echo=FALSE}
JazSpec <- JazSpec %>% 
  mutate(Filename = str_remove(Filename, pattern = " "))  %>% 
  separate(col = Filename, into = c("ObsDate", "MultiCulti", "Par_ue", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE) %>% 
  mutate(FilenameJaz=Filename) %>% 
  select(-c("Filename"))

@@

# Find nm at max count and compare with rolling mean of counts
```{r find nm at max count}
JazSpecTrim <- JazSpecTrim %>% 
  group_by(WL, MultiCulti) %>%
   mutate(rollmeanCounts = zoo::rollmean(Counts, k = RollWindow, align = "left", fill = NA),
          EmMax_nm = round(Wavelength[which.max(Counts)]),
          EmMax_nm_rollmean= round(Wavelength[which.max(rollmeanCounts)])) %>% 
  ungroup()
```

@@

JazSpecNest <- JazSpecTrim %>%
  nest(Spectra = c(Wavelength, Counts, rollmeanCounts))

```{r remove redundant DF}
remove(JazSpecTrim)
remove(JazSpec)
```

@@

JazSpecNest %>%
  unnest(Spectra) %>%
    ggplot() +
  geom_point(aes(x = Wavelength, y = Counts, colour = as.factor(WL))) +
  geom_text(aes(x = EmMax_nm, y= max(Counts), label= EmMax_nm), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  scale_color_manual(values = MCMIXColours) +
  guides(colour = "none") +
  geom_vline(aes(xintercept = EmMax_nm), linetype = "dashed") +
  scale_y_continuous(limits = c(0,100000)) +
  ggh4x::facet_nested(rows = vars(MultiCulti, WL), labeller = labeller(WL = label_both, Par = label_both, MultiCulti = label_both)) +
  theme_bw() 
```

# Cleaning df before saving as rds and removed unnecessary files from the environment
```{r cleaning JazSpecTrim for final rds}
JazSpecNest <- JazSpecNest %>% 
  select(-c(CDateTime))

```{r removed unnecessary files from environment}
rm(JazSpec)
```

@@

```{r save rds}
saveRDS(JazSpecTrim, file.path(DataOut, paste(Project, "Imported_JazEmData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

@@

```{r}
colnames(JazSpecTrim)
```

>>>>

# Set the path to the zip folder
DataIn <- file.path("..", "Data", "RawData", "JazEmData.zip")

RollWindow <- 10

# List files in the extracted folder with a ".txt" extension
Jazfile <- unzip(DataIn, list = TRUE)
Jazfile <- Jazfile[grepl(".txt$", Jazfile$Name), "Name"]
print(Jazfile)
```
# Import MultiCulti actinic par data
```{r read multiculti PAR data}

TargetFile <- "MultiCulti_PAR.csv"

MultiCultiPAR <- read_csv(unz(DataIn, TargetFile)) %>% 
  rename(MultiCulti = "Multiculti")
```

# Set up fread_plus function
```{r set up fread_plus, warning = FALSE, echo=FALSE}
SkipCS <- 14
FileEncodeCS <- "UTF-8"
DelimCS <- "\t"

# Define function to read and process each file
fread_plus <- function(Flnm, Skip, FileEncode, Delim) {
  con <- unz(DataIn, Flnm)  # Connect to the file path within the zip archive
  data <- read.table(con, skip = Skip, encoding = FileEncode, sep = Delim, header = FALSE)

@@

  data <- data %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(DataIn)$ctime)) 
  return(data)
}

@@

# Import and tidy emission data columns
```{r filename separation, warning = FALSE, echo=FALSE}
JazSpec <- JazSpec %>% 
  mutate(Filename = str_remove(Filename, pattern = " "))  %>% 
  separate(col = Filename, into = c("ObsDate", "MultiCulti", "Par_ue", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE) %>% 
  mutate(FilenameJaz=Filename) %>% 
  select(-c("Filename"))

@@

# Find nm at max count
```{r find nm at max count}
JazSpecTrim <- JazSpecTrim %>% 
  group_by(WL, MultiCulti) %>%
   mutate(EmMax_nm = round(Wavelength[which.max(Counts)])) %>% 
  ungroup()
```

# Get 1 mean emission count for each wavelength after rounding for a resolution of 1 nm   
```{r tidy to get one count for each wavelength}
JazSpecTrim <- JazSpecTrim %>% 
   group_by(MultiCulti, Par_ue, WL, Wavelength) %>%
  mutate(MCEm_nm = round(Wavelength)) %>%
  ungroup() %>%
  group_by(FilenameJaz, MultiCulti, Par_ue, WL, MCEm_nm, EmMax_nm, ObsDate) %>%
  summarise(MeanEmission = mean(Counts)) %>%
  ungroup() %>%
  mutate(Emission = round(MeanEmission, digits = 1),
         MC = MultiCulti,
         SetPar_uE = Par_ue,
         MC_SpectralID = paste(MC,WL, sep = "_")) %>% 
  select(-c(MeanEmission))

# Join MulitiCulti par data with emission data
```{r join par with spectral data}
MC_SpectraPAR <- left_join(JazSpecTrim, MultiCultiPAR, by = c("WL" = "Actinic_nm", "SetPar_uE", "MC" = "MultiCulti")) %>%
  rename(MCSetPar_uE = 'SetPar_uE',
         MCMeasuredPar_uE = 'MeasuredPar_uE') %>% 
  select(-c(Par_ue, MultiCulti, Date))

@@

JazSpecNest <- MC_SpectraPAR %>%
  nest(Spectra = c(MCEm_nm, Emission))

```{r remove redundant DF}
remove(JazSpecTrim)
remove(JazSpec)
remove(MC_SpectraPAR)
remove(MultiCultiPAR)
```

@@

JazSpecNest %>%
  unnest(Spectra) %>%
    ggplot() +
  geom_point(aes(x = MCEm_nm, y = Emission, colour = as.factor(WL))) +
  geom_text(aes(x = EmMax_nm, y= max(Emission), label= EmMax_nm), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  scale_color_manual(values = MCMIXColours) +
  guides(colour = "none") +
  geom_vline(aes(xintercept = EmMax_nm), linetype = "dashed") +
  scale_y_continuous(limits = c(0,100000)) +
  ggh4x::facet_nested(rows = vars(MC, WL), labeller = labeller(WL = label_both, Par = label_both, MultiCulti = label_both)) +
  theme_bw()

@@

```{r save rds}
saveRDS(JazSpecNest, file.path(DataOut, paste(Project, "Imported_JazEmData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

@@

```{r}
colnames(JazSpecNest)
```
